The Anthropological Notation Ontology (ANNO): A core ontology for annotating human bones and deriving phenotypes

### 2023-04-14 paper.tex
update 'Ontological Architecture'

  \item ANNOds (\cref{sec:domain}) is a domain ontology for describing domain-specific entities to be used for annotating 
the parts of human skeleton (bones, teeth and landmarks, such as, mandible, left mandibular central secondary incisor tooth 
or mentale dexter) as well as to model their properties and relations (e.g., the distance between mentale dexter and mentale sinister) 
required to derive human phenotypes (e.g., sex or height). The ANNOds is embedded in ANNOdc 
(i.e., the ANNOds classes are subclasses of the ANNOdc classes).

  \item ANNOdc (\cref{sec:core}, \cref{fig:core}) is a core ontology to provide the core entities of a domain, such as, inter alia, 
the general anatomical categories (\enquote{Anatomical structure} and \enquote{Landmark}), categories for describing different characteristics of 
landmarks (\enquote{Landmark location}, \enquote{Landmark property} and \enquote{Landmark line region}) as well as 
the category \enquote{Phenotype} to model the rules for determining human phenotypes. The ANNOdc is founded by \emph{General Formal Ontology} (GFO)~\citep{gfo}.

>>>>

  \item ANNOds (\cref{sec:domain}) is a domain-specific (ds) ontology for describing domain-specific entities to be used for annotating 
the parts of human skeleton (bones, teeth and landmarks, such as, mandible, left mandibular central secondary incisor tooth 
or mentale dexter) as well as to model their properties and relations (e.g., the distance between mentale dexter and mentale sinister) 
required to derive human phenotypes (e.g., sex or height). The ANNOds is embedded in ANNOdc 
(i.e., the ANNOds classes are subclasses of the ANNOdc classes).

  \item ANNOdc (\cref{sec:core}, \cref{fig:core}) is a domain-core (dc) ontology to provide the core entities of a domain, such as, inter alia, 
the general anatomical categories (\enquote{Anatomical structure} and \enquote{Landmark}), categories for describing different characteristics of 
landmarks (\enquote{Landmark location}, \enquote{Landmark property} and \enquote{Landmark line region}) as well as 
the category \enquote{Phenotype} to model the rules for determining human phenotypes. The ANNOdc is founded by \emph{General Formal Ontology} (GFO)~\citep{gfo}.
